---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

[![Travis build status](https://travis-ci.org/heike/extracat.svg?branch=master)](https://travis-ci.org/heike/extracat)


# extracat

`extracat` is an R package for working with categorical variables.


## Installation

The package `extracat` has been archived from CRAN, but you can install it from this github repository:

```{r, eval=FALSE}
devtools::install_github("heike/extracat")
```

## Simple use case

Several data sets are provided within the package, the command `visna` provides a good first overview of the where missing values are in a data set:
```{r}
library(extracat)
visna(GeneEx)
```

Using additional sorting methods, we can work out patterns of missing values:

```{r}
# reorder both rows and columns:
visna(GeneEx, sort = "b", sort.method="optile")
```

